Age-related changes in plant growth and traits

### 2016-06-21 scripts/Growth_figs.rmd
edits to figures

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "growth_leaf"
xvar <- "total_weight_0"

data <- subset(SummaryInd,growth_leaf>0)
data <- split(data, data$species)

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",cex=1.4, xlab="",ylab="",
                    main=spp,col=col.age(data[[spp]]$age))
}

mtext("Investment in leaves (mg)", 2, outer=TRUE,cex=1.2)
mtext("Initial plant weight (mg)", 1, outer=TRUE,cex=1.2)
legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "growth_stem"
xvar <- "total_weight_0"

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",cex=1.4, xlab="",ylab="",
                    main=spp,col=col.age(data[[spp]]$age))
}

mtext("Investment in stems (mg)", 2, outer=TRUE,cex=1.2)
mtext("Initial plant weight (mg)", 1, outer=TRUE,cex=1.2)
legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
```

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "growth_stem_diameter"
xvar <- "growth_shoot_diameter"

@@

mtext("increase in stem diameter (mm)", 2, outer=TRUE,cex=1.2)
mtext("increase in shoot diameter (mm)", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=0.9,bty="n")
```

>>>>

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.4,ylim=c(1)
                    main=spp,col=col.mature(data[[spp]]$mature))
}

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
par(mfrow=c(4,4), cex=1, omi=c(1.1,.5,.1,.1), mai=c(.1,.8,.5,0.1)) 
yvar <- "growth_leaf"
xvar <- "total_weight_0"

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",cex=1.4, xlab="",ylab="",
                    col=col.age(data[[spp]]$age))
  abline(0,0)
  mtext(spp,3,line=0)
}

mtext("Investment in leaves (mg)", 2, outer=TRUE,cex=1.2,line=0)
mtext("Initial plant weight (mg)", 1, outer=TRUE,cex=1.2,line=2)
legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=.8,bty="n")
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
par(mfrow=c(4,4), cex=1, omi=c(1.1,.5,.1,.1), mai=c(.1,.8,.5,0.1))
yvar <- "growth_stem"
xvar <- "total_weight_0"

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",cex=1.3, xlab="",ylab="",
                    col=col.age(data[[spp]]$age))
  mtext(spp,3,line=0)
}

mtext("Investment in stems (mg)", 2, outer=TRUE,cex=1.2,line=0)
mtext("Initial plant weight (mg)", 1, outer=TRUE,cex=1.2,line=2)
legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
```

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
par(mfrow=c(4,4), cex=1, omi=c(1.1,.5,.1,.1), mai=c(.1,.8,.5,0.1))
yvar <- "growth_stem_diameter"
xvar <- "growth_shoot_diameter"

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.3,
                    col=col.age(data[[spp]]$age))
  mtext(spp,3,line=0)
}

mtext("increase in stem diameter (mm)", 2, outer=TRUE,cex=1.2)
mtext("increase in shoot diameter (mm)", 1, outer=TRUE,cex=1.2,line=2)
legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=0.9,bty="n")
```
